Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
don't say 3: including (exact list of items), just say three techniques: these are.

When considering the use of traffic analysis for classification of Internet
communications, three techniques are used. These are: exact matching, heuristic
matching and machine learning \parencite{Zhang:2009p1188}.

>>>>

When considering the use of traffic analysis for classification of Internet
communications, three techniques are used: exact matching, heuristic matching
and machine learning \parencite{Zhang:2009p1188}.
